---
title: "Analysis of Anti-Vaccine Community on Twitter"
output: 
    html_document: 
      toc: true
---

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(ggplot2) # Data visualization
library(readr) # CSV file I/O, e.g. the read_csv function
library(dplyr)
library(reshape2)
library(tidyr)
library(formattable)
library(RColorBrewer)
library(lubridate)
library(networkD3)
library(plotly)
library(cluster)
library(viridis)
library(stringr)
library(listviewer)
knitr::opts_chunk$set(message=FALSE, warning=FALSE, echo = FALSE)
tweets <- rjson::fromJSON(file = "input/temp_2k.json")

```

```{r warning=FALSE, echo=FALSE}
#View(tweets)
#listviewer::jsonedit(tweets, height = "800px", mode = "view")
tws <- tibble(tweet = tweets)
tweets <- tws %>% unnest_wider(tweet)
tweets <- tweets %>% mutate(is_retweet = NA)
for (i in 1:nrow(tweets)) { 
  tweets[i,]=tweets[i,]%>%
  mutate(is_retweet = ifelse(grepl("^\\bRT\\b", tweets[i,2]), "Retweets", "Originaltweets"))
}
```

#Find the influencers
To understand the fanbase, let's look at their number of tweets vs number of follower to get a sense of their activity level and influence.   
Based on k-mean clustering withinness, we segment their user attributes into 4 groups
```{r fig.height=3,fid.width=6, echo=FALSE}
users <- unnest_wider(tweets["user"], user)
#View(users)
fanbase=users%>%
select(name,followers_count,statuses_count)%>%
group_by(name)%>%
summarize(n_follower=max(followers_count),n_tweet=max(statuses_count))

wss <- numeric(15)
for (k in 1:15) {wss[k] <- sum(kmeans(as.matrix(fanbase[, 2:3]), centers=k,nstart=25,iter.max=30)$withinss)}

set.seed(20)
AntiVaxCluster <- kmeans(as.matrix(fanbase[, 2:3]), 4, nstart = 20)
```

Visualize it with a scatter plot
```{r}
scatter=fanbase%>%
ggplot(aes(n_tweet,n_follower))+
geom_point(aes(color=factor(AntiVaxCluster$cluster)))+
geom_text(aes(label=ifelse((n_follower>500000&n_tweet>1000)|(n_follower>50000&n_tweet>100000),as.character(name),'')),vjust=1.5)+
guides(color="none")+
ggtitle('Tweet Activity vs Influence')
ggplotly()
```

##activity types
```{r}
tweets%>%group_by(is_retweet)%>%
summarize(n_tweet=n())%>%
head()
```

##mentions
Let's also top handles mentioned  

```{r mention}
mention=tweets%>%
  mutate(mention=str_extract_all(tweets[["full_text"]], "@\\w+"))%>%
  select(mention)%>%
  filter(!is.na(mention))%>%
  unnest(mention)%>%
  group_by(mention)%>%
  summarize(n_mention=n())%>%
  arrange(desc(n_mention))
mention%>%
  head(10)
```
#extract mention network
```{r warning=FALSE}
library(visNetwork)
user=users%>%
select(screen_name)%>%
unique()
tweets <- tweets %>% mutate(username=users$name)
edges=tweets %>%
  select(from=username, full_text)%>%
  mutate(to = str_extract_all(full_text, '(?<=@)\\w+')) %>%
  filter(to!='character(0)') %>%
  select(-full_text)%>%
  unnest(to)%>%
  mutate(flag=to%in%user$screen_name)%>%
  filter(flag==TRUE)%>%
  select(-flag)%>%
  group_by(from,to) %>% tally()

nodes=data.frame(id=unique( union(unique(edges$from), unique(edges$to))))
nodes$title <-nodes$id
edges$arrows <-'to'
edges$width<- (edges$n)^(1/3)
network <- visNetwork(nodes, edges)%>%
  visOptions(highlightNearest = TRUE)%>%
  visPhysics(stabilization = FALSE)%>%
  visEdges(smooth = FALSE)%>%
  visIgraphLayout()
network
```
#Spectral Clustering of the Network
```{r}
spectral_clustering <- function(X, # matrix of data points
                                nn = 10, # the k nearest neighbors to consider
                                n_eig = 2) # m number of eignenvectors to keep
{
  mutual_knn_graph <- function(X, nn = 10)
  {
    D <- as.matrix( dist(X) ) # matrix of euclidean distances between data points in X
    
    # intialize the knn matrix
    knn_mat <- matrix(0,
                      nrow = nrow(X),
                      ncol = nrow(X))
    
    # find the 10 nearest neighbors for each point
    for (i in 1: nrow(X)) {
      neighbor_index <- order(D[i,])[2:(nn + 1)]
      knn_mat[i,][neighbor_index] <- 1 
    }
   
    # Now we note that i,j are neighbors iff K[i,j] = 1 or K[j,i] = 1 
    knn_mat <- knn_mat + t(knn_mat) # find mutual knn
    
    knn_mat[ knn_mat == 2 ] = 1
    
    return(knn_mat)
  }
  
  graph_laplacian <- function(W, normalized = TRUE)
  {
    stopifnot(nrow(W) == ncol(W)) 
    
    g = colSums(W) # degrees of vertices
    n = nrow(W)
    
    if(normalized)
    {
      D_half = diag(1 / sqrt(g) )
      return( diag(n) - D_half %*% W %*% D_half )
    }
    else
    {
      return( diag(g) - W )
    }
  }
  
  W = mutual_knn_graph(X) # 1. matrix of similarities
  L = graph_laplacian(W) # 2. compute graph laplacian
  ei = eigen(L, symmetric = TRUE) # 3. Compute the eigenvectors and values of L
  n = nrow(L)
  return(ei$vectors[,(n - n_eig):(n - 1)]) # return the eigenvectors of the n_eig smallest eige nvalues

}
coords_x <- network$x$nodes$x
coords_y <- network$x$nodes$y
mdata <- cbind(coords_x, coords_y) # matrix of data points

# do spectral clustering procedure

X_sc <- spectral_clustering(mdata)

# run kmeans on the 2 eigenvectors
X_sc_kmeans <- kmeans(X_sc, 2)

clusters <- X_sc_kmeans$cluster
nodes["cluster"] <- clusters
nodes=data.frame(id=unique( union(unique(edges$from), unique(edges$to))),
                 color=ifelse(nodes$cluster==1,"green", "orange"))

network <- visNetwork(nodes, edges)%>%
  visOptions(highlightNearest = TRUE)%>%
  visPhysics(stabilization = FALSE)%>%
  visEdges(smooth = FALSE)%>%
  visIgraphLayout()
network

```

